\documentclass{article}
\usepackage[utf8]{inputenc}

\title{BrickGame v1.0 README}

\begin{document}

\maketitle

\section{Introduction-Features}
- Classic Tetris gameplay with the following mechanics:
    - Rotation of tetrominoes
    - Horizontal movement of tetrominoes
    - Accelerated tetromino falling (by holding the down arrow key)
    - Display of the next tetromino
    - Line clearing
    - Game over when the tetromino reaches the top of the game field

\section{General info}
- Support for all physical buttons on the console:
    - Start game - ENTER
    - Pause - SPACE
    - End game - ESCAPE
    - Left arrow - move tetromino left
    - Right arrow - move tetromino right
    - Down arrow - accelerate tetromino falling
    - Up arrow - rotate tetromino
- Matrix-based game field with dimensions corresponding to the console's size (10x20 pixels)
- Proper stopping of tetrominoes after reaching the bottom or colliding with another tetromino
- Unit tests for the game logic library, achieving at least 90\% code coverage

\section{Install}
1. Clone the repository.
2. Navigate to the `src/` directory.
3. Run `make install` to install the project.
4. Run `make run` to start playing.

\section{Usage}
- Use the arrow keys to move and rotate tetrominoes.
- Press the down arrow key to make tetrominoes fall faster.
- Press the up arrow key to rotate tetrominoes.

\subsection{Score Calculation}
- 1 line cleared: 100 points
- 2 lines cleared: 300 points
- 3 lines cleared: 700 points
- 4 lines cleared: 1500 points

\subsection{Additional Mechanics}
- Display of the player's current score and highest score achieved
- Highest score is stored in a file or embedded database and persists between game sessions

- Progression of levels every 600 points
- Increasing level increases the speed of tetromino falling


\section{Credits}
Enjoy the game!

\end{document}
